The stopping power of \clau{hydrogen in} hafnium and the importance of relativistic $4f$ electrons

### 2020-04-20 response.tex

%-----------------------------------------------------------------------
\begin{figure}[!t]
\centering
\includegraphics[width=12.cm]{Fig05.eps}
\caption{Total stopping, present results using relativistic and non-relativistic solutions for hafnium atom. Curves and symbols explained inside the figure}
\label{NR}
\end{figure}
%-----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
\vspace{0.25cm}
\textsl{
3. Furthermore, it would also be meaningful to show the results from
the ML(FEG) calculation alone in order to identify better the
contribution of the bound electrons to the SP.}

\vspace{0.1cm}
{\color{red} Thank you for this suggestion. We have added the curves for FEG and bound electrons to Fig. 3, and the corresponding comments in the text and in the figure caption.}

@@

% ----------------------------------------------------------------------
\vspace{0.25cm}
\textsl{
4. When comparing the new and existing experimental data, clarify what
experimental technique was used in Ref. 7 to measure the stopping
power.}

\vspace{0.1cm}
{\color{red} Good suggestion, thank you. Sirotinin group used the backscattering method for these measurements. We have added a sentence in the introduction, last paragraph, and in the second paragraph of section IV related to Fig. 4.}

{\small ''Present measurements using transmission method are in good agreement with the previous data by 
Sirotinin, measured in backscattering geometry''}

@@

% ----------------------------------------------------------------------
\vspace{0.25cm}
\textsl{
5. The data by Sirotonin et al. plotted in Fig. 4 seem to suggest that
the stopping power maximum would be around 100-200 keV, while the
maximum predicted in the present work by the theoretical calculations
is located at slightly smaller energies. Please comment on this point
and discuss possible reasons for this discrepancy: What are the main
limitations in the theoretical model that can be causing this energy
shift?}

\vspace{0.1cm}
{\color{red} The stopping maximum is very sensitive to the theoretical model and to the experimental method. Sirotinin paper mention "possible reasons for the disagreement of the measurement results near the E(E) curve maximum". 
%The original paper by Sirotinin says: "The possible reasons for the disagreement of the measurement results near the E(E) curve maximum are mainly related to the inaccuracy in determining thickness, to nonuniformity of the thickness, and the neglect of the effect of the chemical composition and structure of the thin films used in the measurements"
For targets with many different sets of data (i.e. H in Ag, Al, Au, Fe, Cu, Si, and others) it is usual to note great dispersion of values around the maximum. In the case of Hf, only one set of data is available and it is perfectly matched by SRIM semi-empirical curve. SRIM clearly includes these values in the adjust of the code, so it does not represent a test for this data. One of the goals of this work is to call the attention on possible differences between theory and the existing values, and to remark the necessity of more experimental data in certain energy regions, mainly, the stopping maximum and below. We have changed the comments in page 6 lines 328-336 and lines 364-366 as follows:}

{\small ''Future experiments  would be important to
complete this study on the stopping of Hf for protons. In the energy region $80-500$ keV only the measurements by Sirotinin group in 1984 are available. SRIM clearly includes these values in the adjust of the code, so it does not represent a test for this data. Undoubtedly, new measurements are needed in three specific energy regions: below 500 keV, around the stopping maximum (i.e. $50-200$ keV) and at low impact energies''}

{\small ''Future experiments for impact energies around the stopping maximum and in the low energy region would be important to complete this study.''}

{\color{red} In relation with the referee comment about the maximum of the stopping, in Fig. 4 we have added the comparison with other two theoretical results: CASP and PASS. The following comment has been included in page 6, lines 315-322:}

{\small ''The stopping maximum is a very sensitive region for any full theoretical description, with no parameters at all, and this is quite visible in a linear-scale plot like Fig. [4]. However, the impact energy for the maximum seem to agree between our curve and DPASS, although DPASS is $10 \%$ below ours. Instead, CasP predicts a stopping maximum $10 \%$ above our value and a completely different shape at lower energies.''}

@@

% ----------------------------------------------------------------------
\vspace{0.25cm}
\textsl{
6. When reviewing on the experimental work performed on Hf oxides in
the introduction, note that there is a quite recent work by Roth and
co-workers published in Phys. Rev. Lett. 119, 163401 (2017), in which
the SP of protons is precisely measured in this target.}

\vspace{0.1cm}
{\color{red} We thank the referee for suggesting this missing reference. We have
included it in the revised manuscript.}

@@

% ----------------------------------------------------------------------
\vspace{0.25cm}
\textsl{Finally, there are few misprints in the generated pdf file:}

\textsl{- Y-axis labels in Figs. 3 an 4 are unreadable }

{\color{red} We have changed to larger prints  and have written explicitly "stopping cross section" -Y- and "Impact energy" -X- instead of S(E) and E. }

\textsl{- Page 3,2nd column, 2nd full paragraph: "Too assess"}
{\color{red} corrected}

\textsl{- Caption of Fig.2: "hollow circles" -$>$ "open circles" or
"unfilled circles"}
{\color{red} corrected}
